Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-28 prop_letter.tex
prop_letter.tex Introduction Updating...
prop_letter.tex \paragraph{The Kochen-Specker Theorem} Replace vector by projectors...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
However, it is not evident at all that this resource-aware perspective
does not alter the very foundations of quantum mechanics. In order
to analyze the quantum world with finite resource, we extend the classical
interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
and introduce a new framework: quantum IVPM...\newpage{}

@@

Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
be a quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}_{24}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
\necess & \text{, if }x=1\text{ ;}\\
\imposs & \text{, if }x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
satisfying the following conditions because the right-hand side of
each equation forms an orthogonal basis and we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
\begin{eqnarray}
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
 &  & +\bar{f}(0,0,1,0)+\bar{f}(0,0,0,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,1,0,0)\nonumber \\*
 &  & +\bar{f}(0,0,1,1)+\bar{f}(0,0,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,1,0)\nonumber \\*
 &  & +\bar{f}(0,1,0,1)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,0,0)+\bar{f}(0,0,0,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(0,1,-1,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,-1,1,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(-1,1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(1,0,1,0)+\bar{f}(0,1,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,-1,1,1)+\bar{f}(1,1,-1,1)\nonumber \\*
 &  & +\bar{f}(0,1,1,0)+\bar{f}(1,0,0,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,1,-1,1)+\bar{f}(1,1,1,-1)\nonumber \\*
 &  & +\bar{f}(0,0,1,1)+\bar{f}(1,-1,0,0)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,1,-1,0)+\bar{f}(1,0,0,-1)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,-1,-1,1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(0,0,1,-1)+\bar{f}(1,-1,0,0)\nonumber \\*
 &  & +\bar{f}(1,1,1,1)+\bar{f}(1,1,-1,-1)\textrm{ ,}\\
\necess & \subseteq & \bar{f}(1,0,1,0)+\bar{f}(0,1,0,1)\nonumber \\*
 &  & +\bar{f}(1,1,-1,-1)+\bar{f}(1,-1,-1,1)\textrm{ .}
\end{eqnarray}
\end{subequations}If we sum up Eq.~(\ref{eq:Kernaghan}), we will
have
\begin{eqnarray}
\left[11,11\right] & \subseteq & 4\bar{f}(1,0,0,0)+4\bar{f}(1,1,-1,1)\nonumber \\
 &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
\end{eqnarray}
where 
\begin{eqnarray}
\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{(1,0,0,0),(1,1,-1,1),(1,-1,1,-1),\nonumber \\
 &  & (1,0,-1,0),(1,0,0,1),(1,1,0,0)\}\textrm{ .}
\end{eqnarray}
However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
can never be satisfied. Because each term in right-hand side is either
$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the right-hand
side is a singleton set of an even integer while the left-hand side
is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
Moreover, there is no quantum IVPM defined on the set of all projectors
as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then we can restrict $\bar{\mu}$ and define $\bar{\mu}_{24}=\left.\bar{\mu}\right|_{\events_{24}}$.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that an perfect measurement
cannot be performed, and real measurements must be finite precision.
In this paper, we model the quantum finite precision by quantum interval-valued
probability measures (IVPMs). Under this framework,

Following Feynman~\cite{Feynman1982Simulating}, Landauer~\cite{Landauer1996188},
and others, one might argue that this resource-bounded perspective
is also crucial for understanding the very nature of physical processes.
However, it is not evident at all that this resource-aware perspective
does not alter the very foundations of quantum mechanics. In order
to analyze the quantum world with finite resource, we extend the classical
interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
and introduce a new framework: quantum IVPM...\newpage{}

@@

Assume there is a function~$v:\events_{24}\rightarrow\left\{ 0,1\right\} $
satisfying equation~(\ref{eq:Kochen-Specker-Rules}). There must
be a quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{\mu}_{24}\left(P\right)=\iota_{\mathrm{D}}\left(v\left(P\right)\right)$,
where 
\begin{equation}
\iota_{\mathrm{D}}\left(x\right)=\begin{cases}
\necess & \text{, if }x=1\text{ ;}\\
\imposs & \text{, if }x=0\text{ .}
\end{cases}\label{eq:homomorphism-0}
\end{equation}
Hence, there exists an interval-valued frame function~$\bar{f}:\mathcal{T}_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$
defined by $\bar{f}\left(\ket{\psi}\right)=\bar{\mu}_{24}\left(\proj{\psi}\right)$
satisfying the following conditions because the right-hand side of
each equation forms an orthogonal basis and we can apply Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})\begin{subequations}\label{eq:Kernaghan}
\begin{eqnarray}
\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{01}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{10}\right)+\bar{f}\left(P_{11}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{01}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{1\ps}\right)+\bar{f}\left(P_{1\ms}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{10}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\ps1}\right)+\bar{f}\left(P_{\ms1}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{00}\right)+\bar{f}\left(P_{11}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\textrm{B}0}\right)+\bar{f}\left(P_{\textrm{B}1}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{\textrm{N}3}\right)+\bar{f}\left(P_{\textrm{N}2}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\textrm{N}1}\right)+\bar{f}\left(P_{\textrm{N}0}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{\textrm{N}3}\right)+\bar{f}\left(P_{\textrm{N}1}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\ps0}\right)+\bar{f}\left(P_{\ms1}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{\textrm{N}2}\right)+\bar{f}\left(P_{\textrm{N}1}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\textrm{B}0}\right)+\bar{f}\left(P_{\textrm{B}3}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{\textrm{N}1}\right)+\bar{f}\left(P_{\textrm{N}0}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{1\ps}\right)+\bar{f}\left(P_{0\ms}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{\textrm{B}1}\right)+\bar{f}\left(P_{\textrm{B}3}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\ps\ps}\right)+\bar{f}\left(P_{\ms\ms}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{1\ms}\right)+\bar{f}\left(P_{0\ms}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\ps\ps}\right)+\bar{f}\left(P_{\ms\ps}\right)\textrm{ ,}\\
\necess & \subseteq & \bar{f}\left(P_{\ps0}\right)+\bar{f}\left(P_{\ps1}\right)\nonumber \\*
 &  & +\bar{f}\left(P_{\ms\ps}\right)+\bar{f}\left(P_{\ms\ms}\right)\textrm{ .}
\end{eqnarray}
\end{subequations}If we sum up Eq.~(\ref{eq:Kernaghan}), we will
have
\begin{eqnarray}
\left[11,11\right] & \subseteq & 4\bar{f}\left(P_{00}\right)+4\bar{f}\left(P_{\textrm{N}1}\right)\nonumber \\
 &  & +2\sum_{\ket{\psi}\in\mathcal{T}_{18}}\bar{f}\left(\ket{\psi}\right)\textrm{ ,}\label{eq:QuantumInterval-valuedProbability-Total}
\end{eqnarray}
where 
\begin{eqnarray}
\mathcal{T}_{18} & = & \mathcal{T}_{24}\backslash\{\left(P_{00}\right),\left(P_{\textrm{N}1}\right),\left(P_{\ps\ms}\right),\nonumber \\
 &  & \left(P_{\ms0}\right),\left(P_{\textrm{B}2}\right),\left(P_{0\ps}\right)\}\textrm{ .}
\end{eqnarray}
However, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Total})
can never be satisfied. Because each term in right-hand side is either
$\imposs=\left[0,0\right]$ or $\necess=\left[1,1\right]$, the right-hand
side is a singleton set of an even integer while the left-hand side
is $\left\{ 11\right\} $. Therefore, there is no quantum IVPM~$\bar{\mu}_{24}:\events_{24}\rightarrow\mathscr{I}_{\mathrm{D}}$.
Moreover, there is no quantum IVPM defined on the set of all projectors
as well; otherwise, if we have a quantum IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}_{\mathrm{D}}$,
then we can restrict $\bar{\mu}$ and define $\bar{\mu}_{24}=\left.\bar{\mu}\right|_{\events_{24}}$.
